%!TEX root = ../report.tex

\begin{document}
    \begin{abstract}
        Many safety-critical applications like autonomous driving use Deep Neural Networks (DNNs) for object detection and segmentation.
        These DNNs are trained on a dataset with a limited number of classes. 
        This closedness of the dataset will lead to misdetection when the trained DNN encounter unknown data in the real world.
        Typically, this unknown data is called as Out-of-Distribution (OOD) data.
        When the autonomous driving agent encounters the OOD data, these misdetections might lead to catastrophic consequences.
        So it is predominantly important to detect the OOD data.

        Existing OOD detection methods have been extensively studied in the image domain and have not been explored much in the 3D domain.
        In this thesis, we proposed two 3D benchmark datasets, adapt and evaluate the OOD detection methods on the proposed benchmark datasets.
        So, we performed a state-of-the-art analysis on 3D datasets and 3D semantic segmentation models.
        From the analysis, the proposed two 3D benchmark datasets for OOD detection are Semantic3D-vs-S3DIS (outdoor-vs-indoor) with Semantic3D as the In-Distribution (ID) dataset and S3DIS as the OOD dataset.
        The second benchmark dataset is Semantic3D-vs-Semantic3D without colour with Semantic3D without colour being OOD dataset.
        We used Maximum Softmax Probability (MSP) and uncertainty (entropy) based OOD detection methods for this study.
        For uncertainty quantification, we used Deep Ensembles, Flipout and Dropout on the RandLA-Net model.

        We observe that Deep Ensembles outperform other methods in OOD detection with AUROC scores of 0.879 and 0.778 using MSP in both the 3D benchmark datasets respectively.
        Both the MSP and entropy scores from Deep Ensembles were able to detect OOD with high AUROC scores for the first benchmark dataset (Semantic3D-vs-S3DIS), this is because of the huge differnces in point geometry between both the datasets.
        Whereas in the case of the second benchmark dataset (Semantic3D-vs-Semantic3D without colour), MSP and entropy scores from Deep Ensembles struggle to detect OOD data.
        This is because both the Semantic3D and Semantic3D without colour datasets have the same point geometry but different colour values.
    \end{abstract}
\end{document}
